Practical Passphrase Cracking

### 2018-01-12 proposal/proposal.tex
Proposal: processed feedback

Most of user data is password protected, but the choice of these passwords is
largely left to users. Password recommendations propose using hard-to-remember
patterns in order to make it harder to guess, while in reality many of those
`random' tweaks (such as a number or exclamation mark at the end) are easily
iterable by a computer.

Using passphrases, users can approach the problem differently: form a string of
random, common words. The most famous example is `correct horse battery
staple': four words with no coherence, but many people in the field can recall
this phrase without ever trying to memorize it\cite{own}. Studies also show
that users have fewer difficulties when memorizing a passphrase than when
memorizing equally-strong random
passwords\cite{behavioral-analysis}\cite{pwd-memorability}.

Labrande\cite{crackmeimfamous} showed that at least 4 million in a set of 139
million passwords (2.9\%) consist of phrases from publicly available sources.
The exact percentage of passphrases used as passwords is not known, but this
shows they are used by a lof of users while they have been studied relatively
little.

@@

To achieve this, we will use a probabilistic method which generates phrases in
decreasing likelihood. An important factor in this design is the speed at which
it can do this: most methods are not designed to iteratively list all
possibilities in decreasing likelihood, which makes it difficult to do so using
methods such as context-free grammar (as described by
Weir\cite{probabilistic-thesis}, p. 84--85).

@@

@@

The software will work for a general population and cannot be primed with facts
such as birth dates of specific users. In our previous work\cite{own}, we found
this to be not as effective as expected. It seems better to focus on the
general method in this limited-time project.

@@

For software, we expect to use only free and open source products.

>>>>

Requirements for secure passwords are getting more and more stringent. Using
passphrases, users can approach the problem differently: form a string of
random, common words. The most famous example is `correct horse battery
staple': four words with no coherence, but many people in the field can recall
this phrase without ever trying to memorize it\cite{own}. Studies also show
that users have fewer difficulties when memorizing a passphrase than when
memorizing equally-strong random
passwords\cite{behavioral-analysis}\cite{pwd-memorability}.

@@

To achieve this, we will use a probabilistic method which generates phrases in
decreasing likelihood. Which method to use, is part of the research. An
important factor in this design is the speed at which it can do this: most
methods are not designed to iteratively list all possibilities in decreasing
likelihood, which makes it difficult to do so using methods such as
context-free grammar (as described by Weir\cite{probabilistic-thesis}, p.
84--85).

@@

Possible probabilistic approaches are Markov chains, weighted context-free
grammar and neural networks. These methods have been applied to password
cracking in the past, and might be applied to passphrases as well. Markov
chains is one example which has also been applied to
passphrases\cite{sparell-simovits} with good results.

@@

The software will work for a general population and cannot be primed with facts
such as birth dates of specific users. In our previous work\cite{own}, we found
this to be not very effective in passphrases.

@@

For software, we expect to use only free and open source products. We will also
publish our product as free and open source software.
